Stability of flower visitation rate over time is driven by the asynchrony of pollinator abundances but does not determine the stability of plant reproductive success.

### 2023-04-20 Manuscript/Manuscript.Rmd
.

---
title: "Stability of flower visitation rate over time is driven by asynchrony of pollinator abundances but does not determine the stability of plant reproductive success."
author: "Estefanía Tobajas, Virginia Domínguez-García, Francisco P. Molina, Ignasi Bartomeus"
date: '2022-10-26'
output:
  pdf_document:
    latex_engine: xelatex
  word_document: default
header-includes: \usepackage{float} \floatplacement{figure}{H} \usepackage{caption}
  \renewcommand{\caption}{Figure}
bibliography: library.bib
csl: journalofecol.csl
editor_options:
  markdown:
    wrap: sentence
---

@@

1.  The stability of ecological communities over time, often quantified using its aggregated abundance or biomass, is mainly influenced by species richness and the asynchrony of the species fluctuations.
    However, the relation with the stability of ecosystem functioning provided by this community is less explored, specially for functions involving several trophic levels such as plant pollination.
    Understanding the mechanisms driving community stability and whether this stability should be related to the stability of ecosystem functions provided is important for predicting the resilience of communities to changes in biodiversity.

2.  Using a 5-year dataset across 13 Mediterranean shrub patches, we assessed the effect of the richness and asynchrony of pollinators as drivers of the stability of plant's visitation rate and plants reproductive success.
    In addition, we analyzed whether the effects of species richness and visitation rate on plant reproduction success were consistent among years.

3.  The stability of plant's visitation rate is driven by the asynchrony of pollinator species abundances but not by the pollinator richness.
    In contrast, the stability of the plant reproductive success is not related to the stability of the visitation rate.
    A year by year analysis revels that plants are unlikely to be limited by pollinator abundances except in specific years. [extreme low levels of pollinator activity](esto es así Molaria- esto no podemos asegurarlo, al mirar la riqueza y tasa de visitas en los diferentes años es bastante similar)

4.  CONCLUSION

@@

Temporal stability is defined as the capacity of an ecosystem to dampen environmental perturbations over time while retaining ecological functions of interest [@Ives2007; @Pimm1984].
The temporal stability of community can be influenced by the diversity of species present and the asynchrony on the species abundance fluctuations.
A higher number of species might stabilize community level functions by increasing the range of species level potential responses to environmental changes (i.e. the portfolio effect) [@McCann2000; @Tilman2006; @Hector2010; @Xu2021], although non-significant relationships between diversity and stability have also been observed [@Hooper2005; @VanderPlas2019].
Species asynchrony represents the intrinsic differences in species response to disturbances and natural fluctuations [@Loreau2013] which has been suggested as a key driver for community temporal stability [@Loreau2008].
In this sense, higher levels of asynchrony stabilize the community [@Ruijven2007; @Bluthgen2016; @Craven2018]. Species asynchrony has been found to be a factor driving positive relationships between diversity and stability [@Loreau2008;@Xu2015] or even that stability is often more strongly associated with the degree of asynchrony across species than with species richness [@Bluthgen2016;@Huang2020]. Other studies have indicated that temporal stability of the dominant species or asynchrony among these dominant species is important in maintaining the stability of ecosystems [@Sasaki2011; @Valencia2020]. While community temporal stability should be related to the stability of ecosystem functions and services provided by such community, there is limited evidence linking both processes on multitrophic systems.

Since the reproductive success of most plant species highly depends on pollination by animals [@Ollerton2011], the stability of pollinator communities may increase the stability of plant reproductive success.
A greater diversity of pollinators has been shown to increase plant reproductive success as a result of complementary in service provision arising from variation of pollinator effectiveness across space and time [@Hoehn2008; @Frund2010; @Albrecht2012; @Bluthgen2011; @Frund2013].
For example, pollinator species may exhibit different ranges of temporal activity [@Pisanty2016; @Rader2016] and consequently may provide pollination services at different times of the day or of the season.
While some studies report that sites with higher visitation rates show higher plant reproductive outputs [@Garibaldi2013; @Kaiser-Bunbury2017], other studies do not find such relationship [@Hegland2012; @Lundgren2013].
Interestingly, studies looking at pollen limitation show that sites with higher visitation rates show no pollen limitation, indicating than above a certain threshold, changes in visitation rates are no longer relevant [Fig. 1; @Cosacov2008; @Williams2013].
However, the occurrence and magnitude of pollen limitation can vary among years for individual populations [@Burd1994; @Ashman2004], primarily because of variation in pollinator service [@Aizen2007].

```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 8,fig.width=10,out.width="60%",fig.align='center', fig.cap =" 1. Conceptual figure showing the general relationship between visitation rate of pollinators and plant reproductive success to different species richness. As the number of visits from pollinators increases, the plant reproductive success is expected to increase until than above a certain threshold, changes in visitation rates are no longer relevant to plant reproductive success."}
library(ggplot2)
library(patchwork)

@@

Here, [we use a 5-year dataset collected for a total of 12 plant species across 13 Mediterranean woodland patches but to study the role of pollinator richness and asynchrony as drivers of stability of its visitation rates we use the 5 most represented plant species.](no se si asi se entendera que tenemos un total de 12 especies pero que para la estabilidad solo empleamos 5)
Further, we evaluate whether more stable pollinator communities foster a more stable plant reproductive success along years, measuring both the stability of fruit and seed set.
We expect that the stability of visitation rates will increase with higher richness and asynchrony of pollinators.
In addition, a greater stability of plant reproductive success is expected with higher stability of visitation rate.
However, given the lack of a clear relationship between pollinator and plant reproductive output stability, we further analyzed the variability on the yearly effect of pollinator richness and visitation rate on the reproductive success of the plants.

@@

Our study was conducted in the southwest of the Iberian Peninsula (Huelva and Sevilla - Spain).
We selected 13 sites in Mediterranean shrub ecosystems that ranged from sites with little to no disturbances to more modified ones with crops and urban areas nearby.
These sites are similar in the plant community composition and the most abundant plant species are known to be attractive to flower visitors and to depend on pollinators to maximize its reproduction (e.g. dominated by *Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*).
Each site was surveyed at least 7 times per year during the flowering season from 2015 to 2019 (from March to June).
Within each site, we selected 3-4 individuals belonging to 3-9 plant species (mean ± standard error: 5.92 ± 0.54 plant species per site).
We performed focal observations where all the floral visitors (from now on referred to as pollinators) that contacted with their flowers were registered.
Only pollinators that could not be identified in the field were captured, stored, and identified to species level in the laboratory.
For each plant individual, we counted the total number of flowers observed in each survey and at the end of the season, we recorded the number of fruits developed and the number of seeds per fruit in a subsample of [3 fruits.](en algunos casos solo habia contado para dos frutos pero la mayoria son 3)
Focal observations had a duration of five minutes per individual in 2015-2016 and three minutes from 2017 to 2019.
Hence, for each plant individual, the sampling effort was standardized in number of visits per flower per minute.
To that end, we divided the total visits observed by the number of flowers observed and by the total observation time (time observation multiplied by number of survey per year).
Pollinator richness is calculated as the number of pollinator species observed visiting the plant, fruit set as the proportion of fruits developed, and the seed set as the mean number of seeds per fruit for each plant individual sampled per site.

@@

We analyze five plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) that were recorded in at least 5 sites in a minimum of two years per site.
The stability of pollinator visitation rates was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following Tilman, 1999.
To examine the role of richness and synchrony of pollinator species abundances as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot.
The synchrony index for each plant species in the plot was calculated following Loreau and de Mazancourt (2008), as:
$$
\begingroup\Large
\phi =\frac{\sigma_{x_T}^2}{(\sum_{i=1}^S\sigma_{x_i})^2}
\endgroup
$$ where ${\sigma_{x_T}^2}$ is the variance of the community abundance of each plot and ${\sigma_{x_i}}$ is the standard deviation of species i abundance in a community with S species.
This synchrony measurement varies from zero, when fluctuations are perfectly asynchronous, to one, when fluctuations are perfectly synchronous [@Loreau2008].
Finally, we express asynchrony as $1-\phi$.
We also calculated the stability of fruit proportion and of the seed number for each plant species in each plot.

@@

To study whether the stability of the visitation rate influenced in the stability of the plant reproductive success, we run linear mixed models using as response variables the stability of fruit proportion or the stability of seed number and as explanatory variable the visitation rate stability.
Site and plant species were included as factor random.

Finally, we further analyzed the variability on the yearly effect of pollinator richness and visitation rate on the reproductive success of the plants. For this we employed all plant species sampled and we analyzed the interactive effect between richness and year, and between visitation rate and year on fruit proportion using binomial generalized linear mixed model, and on the number of seeds employing linear mixed model. *P* values were obtained using the type III Anova (package: car)
The number of seeds per fruit was centered and scaled per plant species to allow meaningful comparisons across species.
For all models, we included plant species identity nested within site and site as random effects because of multiple individuals of the same plant species are measured at each site.

@@

Stability of visitation rates ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 species (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
There is a strong positive relationship between stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increases [(Estimate ± standard error: 2.903 ± 1.134; *p* = 0.017) (Fig 2A)](Virginia me ha comentado en reportar el R2 de los modelos pero al tratarse de modelos mixtos tendriamos que poner el marginal o el condicional.He revisado articulos que utilizan estos modleos y normalmente no ponen R2. Lo incluyo??), whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063; *p* = 0.986) (Fig 2B).
We also found a positive relationship between asynchrony and pollinator richness (0.020 ± 0.005, *p* = 0.001) (Fig 2C).
Furthermore, we observed one data point has a high leverage on the stability analysis (*C.crispus*, Fig 2A-B), when we remove this point, although the relationship is not significant, the tendency is still positive (0.968 ± 0.745; *p* = 0.215).

@@

Stability of fruit proportion varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged 1.28 to 55.86 (7.018 ± 1.441).
When we analyzed whether the stability of the pollinator's visitation rate affected the stability of the plant reproductive success, we did not find a clear relationship when analyzing the fruit proportion (Estimate ± standard error: -1.547 ± 2.611; *p* = 0.558) (Fig 3A).
However, contrary to expected, the stability of seed number did show a negative relationship with the stability of pollinator's visitation rate (-1.887 ± 0.959; *p* = 0.061) (Fig 3B).Although this tendency is influenced by a high value in the stability of seed number of *H. halimifolium* (Fig 3B) since when we removed this point the relationship disappears (0.561 ± 0.535; *p* = 0.306).

@@

For analyses whether the variability of pollinator richness and visitation rate across years affected to the reproductive success of plants we employed total plant species sampled.
When we analysed the fruit proportion, we found that the interaction between year and pollinator richness, and year and visitation rate affected the fruit proportion (richness and year: $\chi 2$ =  28.976, df = 4, *p* = \<0.0001; visitation rate and year: $\chi 2$ =  40.691, df = 4, *p* = \<0.0001). Furthermore, we observed a significant effect of year by itself, not so of pollinator richness or visitation rate.
Although we observed a general saturation of the proportion of fruits developed with most species consistently over 80% of fruit set, in years like 2017 we found that a greater richness and visitation rate increased the fruit proportion.
We also observed a positive relationship between richness and fruit proportion in 2019.
However in 2018, the relationship between richness and fruit proportion was negative (Fig 3).
[esto requiere un poco más de story telling.Por ejemplo, estos años son años altos o bajos en polinizadores?](con los datos que tenemos la riqueza y la tasa de visitas es similar en los diferentes años. Tambien he mirado datos meteorologicos descargados de la estacion de Almonte-precipitacion, radiacion, humedad y temperatura,y no parace que haya diferencias entre años)

For the seed number, we found an effect of year in both models in addition to the interaction between visitation rate and year ($\chi 2$ =  9.113, df = 4, *p* = 0.058) but not the interaction between pollinator richness and year ($\chi 2$ =  2.592, df = 4, *p* = 0.628). 
We observed that a higher visitation rate increased the seed number in 2019 (Supplementary material-Fig 2).

@@

We show that pollinator's visitation rate stability increase with higher asynchrony of pollinators species abundances and that greater species richness only increase stability of visitation rate indirectly, via enhanced species asynchrony.
However, contrary to expectations, we found no relationship between the stability of visitation rates and the stability of plant reproductive success.
This is because in our study system, plant reproduction is not pollinator limited in most years, with most plants reaching maximum reproductive success even in the sites with [lower pollinator abundances.](quizas decir lower richness and visitation rate??)
However, this do not imply that pollinators are not important or that are always in enough numbers to disregard them, because for specific years the relationship between pollinator activity and plant's reproductive output kicks in as important.[seria ideal decir quales... los que tienen poco polinizador? Los secos, quizas?](los años no tienen menor actividad ni riqueza de polinizadores, tampoco son los años mas secos, no se ven diferencias en precipitacion, temperatura, humedad o radiacion)
When and where pollinators are limiting is the key question then.
[esta frase a lo mejor puede ser una conclusing sentence del paper, por ahora la dejo aquí]

While drivers of temporal stability have been well study in plant communities [@Ruijven2007; @Gross2014; @Craven2018; @Leps2018; @Sasaki2019; @Valencia2020; @Kigel2021], relatively few studies have evaluated how this same drivers can affect community stability in mobile organisms such as pollinators [@Ebeling2008; @Senapathi2021; @Lazaro2022].
A first outcome of our analysis is that asynchrony of species abundances is a key driver of visitation rate stability.
This stability-asynchrony relationship has been found by different theoretical and empirical studies [@DeMazancourt2013; @Bluthgen2016; @Leps2018; @Sasaki2019; @Valencia2020; @Kigel2021].
For example, Lázaro et al.(2022) also found for plants, pollinators and their interactions that more asynchronous communities being more temporal stable.
In this sense, species asynchrony can increase temporal stability of visitation rate when the abundance of one species increases as a result of decreases in the abundance of another species, density compensation [@Winfree2009a; @Mukherjee2019]; or also in response to the same environmental changes, response diversity [@Walker99; @Winfree2013].[Aunque nosotros no sabemos si estos cambios son debido a perturbaciones ambientales, We believe it is important to test the degree to which these stabilizing mechanisms are at work.](Quizas añadir algo asi??)

On the other hand, species richness is considered one of the strongest drivers of community stability in plants [@Tilman2006; @Hallett2014], although Valencia et al. (2020), analyzing a large number of plant community datasets, have reported that this relationship is not as strong.
Pollinator studies, carried out in crop systems, have observed a positive relationship between species richness and stability of floral visits [@Ebeling2008] or stability of abundance and richness [@Senapathi2021]. However, our results show that pollinator richness was positively associated with asynchrony, which might positively affect the stability of visitation rate, but indirectly. Species richness may increase the probability that community contains species with different responses to environmental conditions and perturbations, leading to asynchrony (compensation) among species abundance and thus, to an increase in community stability [@Craven2018; @McCann2000; @Yachi1999].

>>>>

---
title: "Stability of flower visitation rate over time is driven by the asynchrony of pollinator abundances but does not determine the stability of plant reproductive success."
author: "Estefanía Tobajas^1, Virginia Domínguez-García^1, Francisco P. Molina^1, Ignasi Bartomeus^1"
date: '2022-10-26'
output:
  pdf_document:
    latex_engine: xelatex
  word_document: default
header-includes: \usepackage{float} \floatplacement{figure}{H} \usepackage{caption}
  \renewcommand{\caption}{Figure}
bibliography: library.bib
csl: journalofecol.csl
editor_options:
  markdown:
    wrap: sentence
---

\^1 Estación Biológica de Doñana (EBD-CSIC).
Sevilla, Spain.

@@

1.  The stability of ecological communities over time, often quantified using its aggregated abundance or biomass, is though to be influenced by species richness and the asynchrony of the species fluctuations.
    However, the relation between community stability and the stability of the ecosystem functioning provided by this community is less explored, specially for functions involving several trophic levels such as plant pollination.
    Understanding the mechanisms driving community stability and whether this stability should be related to the stability of ecosystem functions provided is important for predicting the resilience of communities to changes in biodiversity.

2.  Using a 5-year dataset across 13 Mediterranean shrublands and X plant species, we assessed the effect of pollinator richness and asynchrony as drivers of the stability of plant's visitation rate and plants reproductive success.
    In addition, we analyzed whether the effects of species richness and visitation rate on plant reproduction success were consistent among years.

3.  The stability of plant's visitation rate is driven by the asynchrony of pollinator species abundances but not by the pollinator richness.
    In contrast, the stability of the plant reproductive success is not related to the stability of its pollinator visitation rates.
    A year by year analysis revels that plants are unlikely to be limited by pollinator abundances except in specific years.

4.  We highlight the importance of maintaining a redundancy of pollinators that visit the same plant species, given that its presence can buffer from species temporal fluctuations.
    This is particularly important for pollinators with contsarting responses to environmental fluctuations, as this creates the needed asynchrony of their populations to guarantee stable levels of flower visitation rates.
    However, we warn that more complex ecosystem functions such as reproductive success, which not only depends on pollinators, but on plant competition or resource availability, might be decoupled from primary functions (i.e. visitation rates and pollen deposition) when pollination is not a limiting factor.

@@

Temporal stability is defined as the capacity of an ecosystem to dampen environmental perturbations over time while retaining ecological functions of interest [@Ives2007; @Pimm1984].
The temporal stability of a community can be influenced by the diversity of species present and the asynchrony on the species abundance fluctuations.
A higher number of species might stabilize community level functions by increasing the range of species level potential responses to environmental changes (i.e. the portfolio effect) [@McCann2000; @Tilman2006; @Hector2010; @Xu2021], although non-significant relationships between diversity and stability have also been observed [@Hooper2005; @VanderPlas2019].
Species asynchrony represents the intrinsic differences in species response to disturbances and natural fluctuations [@Loreau2013] which has been suggested as a key driver for community temporal stability [@Loreau2008].
In this sense, higher levels of species asynchrony stabilize the overall community dynamics [@Ruijven2007; @Bluthgen2016; @Craven2018].
Species asynchrony has been found to be a factor driving positive relationships between diversity and stability [@Loreau2008; @Xu2015] or even that stability is often more strongly associated with the degree of asynchrony across species than with species richness [@Bluthgen2016; @Huang2020].
Other studies have indicated that temporal stability of the dominant species or asynchrony among these dominant species is important in maintaining the stability of ecosystems [@Sasaki2011; @Valencia2020].
While community temporal stability should be related to the stability of ecosystem functions and services provided by such community, there is limited evidence linking both processes on multitrophic systems.

Since the reproductive success of most plant species highly depends on pollination by animals [@Ollerton2011], the stability of pollinator communities may increase the stability of plant reproductive success.
A greater diversity of pollinators has been shown to increase plant reproductive success as a result of complementary in service provision arising from variation of pollinator effectiveness across space and time [@Hoehn2008; @Frund2010; @Albrecht2012; @Bluthgen2011; @Frund2013; @Magrach2021].
For example, pollinator species may exhibit different ranges of daily temporal activity [@Pisanty2016; @Rader2016, @zaragoza-trello2023] and consequently may provide pollination services at different times of the day or of the season.
In any case, higher overall visitation rates are often assumed to insure reproductive success.
However, while some studies report that higher visitation rates are correlated with higher plant reproductive outputs [@Garibaldi2013; @Kaiser-Bunbury2017, @vázquez2005], other studies do not find such relationship [@Hegland2012; @Lundgren2013].
Interestingly, studies looking at pollen limitation show that higher visitation rates are often associated with no pollen limitation, indicating than above a certain threshold, changes in visitation rates are no longer relevant [Fig. 1; @Cosacov2008; @Williams2013].
However, the occurrence and magnitude of pollen limitation can vary among years for individual populations [@Burd1994; @Ashman2004], primarily because of variation in pollinator service [@Aizen2007].

```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 8,fig.width=10,out.width="60%",fig.align='center', fig.cap =" 1. Conceptual figure showing the general relationship between visitation rate of pollinators and plant reproductive success to different species richness (R1, R2, ...). As the number of visits (V1, V2, ...) from pollinators increases, the plant reproductive success is expected to increase until than above a certain threshold, changes in visitation rates are no longer relevant to plant reproductive success."}
library(ggplot2)
library(patchwork)

####IB: ESTEFANIA, necesitamos un A y B en plots de abajo, para que la gente los reconozca. EN esos paneles yo escribiria Repreocution y Visitation /Richness entro. Y los paneles A y B necesitan explicación en la leyenda, de hecho, yo creo que ahora estan girados... o eso o estoy espeso. Lo hablamos por video.

@@

Here, we use a 5-year dataset collected for a total of 12 plant species across 13 Mediterranean shrubland sites.
However, to study the role of pollinator richness and asynchrony as drivers of stability of its visitation rates we only use the 5 most represented plant species across years and sites.
Further, we evaluate whether more stable pollinator communities foster a more stable plant reproductive success along years, measuring both the stability of fruit and seed set.
We expect that the stability of visitation rates will increase with higher richness and asynchrony of pollinators.
In addition, a greater stability of plant reproductive success is expected with higher stability of visitation rates.
However, given the lack of a clear relationship between pollinator and plant reproductive output stability, we further analyzed the variability on the yearly effect of pollinator richness and visitation rate on the reproductive success of the plants.

@@

Our study was conducted in the southwest of the Iberian Peninsula (Huelva and Sevilla - Spain).
We selected 13 sites in Mediterranean shrub ecosystems that ranged from sites with little to no disturbances to more modified ones with crops and urban areas nearby.
These sites are similar in the plant community composition and the most abundant plant species are known to be attractive to flower visitors and to depend on pollinators to maximize its reproduction (e.g. dominated by *Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*).
Each site was surveyed at least 7 times per year during the flowering season from 2015 to 2019 (from March to June).
Within each site, we selected 3-4 individuals belonging to 3-9 plant species (mean ± standard error: 5.92 ± 0.54 plant species per site).
We performed focal observations where all the floral visitors (from now on referred to as pollinators) that contacted with their flowers were registered.
Only pollinators that could not be identified in the field were captured, stored, and identified to species level in the laboratory.
For each plant individual, we counted the total number of flowers observed in each survey and at the end of the season, we recorded the number of fruits developed / aborted and the number of seeds per fruit in a subsample of 3 fruits.
Focal observations had a duration of five minutes per individual in 2015-2016 and three minutes from 2017 to 2019.
Hence, for each plant individual, the sampling effort was standardized to the number of visits per flower per minute.
To that end, we divided the total visits observed by the number of flowers observed and by the total observation time (time of each observation multiplied by number of survey rounds per year).
Pollinator richness is calculated as the number of pollinator species observed visiting the plant, fruit set as the proportion of fruits developed, and the seed set as the mean number of seeds per fruit for each plant individual sampled per site.

@@

We analyze five plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) that were recorded in at least 5 sites in a minimum of two years per site.
The stability of pollinator visitation rates was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following Tilman, 1999.
This is an adequate index given that in our dataset the mean and the variance scale with each other.
To examine the role of richness and synchrony of pollinator species abundances as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot.
The synchrony index for each plant species in the plot was calculated following Loreau and de Mazancourt (2008), as: $$
\begingroup\Large
\phi =\frac{\sigma_{x_T}^2}{(\sum_{i=1}^S\sigma_{x_i})^2}
\endgroup
$$ where ${\sigma_{x_T}^2}$ is the variance of the community abundance of each plot and ${\sigma_{x_i}}$ is the standard deviation of species i abundance in a community with S species.
This synchrony measurement varies from zero, when fluctuations are perfectly asynchronous, to one, when fluctuations are perfectly synchronous [@Loreau2008].
Finally, we express asynchrony as $1-\phi$.
We also calculated the stability of fruit proportion and of the seed number for each plant species in each plot.

@@

To study whether the stability of pollinator visitation rate influenced in the stability of the plant reproductive success, we run linear mixed models using as response variables the stability of fruit proportion or the stability of seed number and as explanatory variable the visitation rate stability.
Site and plant species were included as random factors.

Finally, we further analyzed the variability on the yearly effect of pollinator richness and visitation rate on the reproductive success of the plants.
For this we employed all plant species sampled and we analyzed the interactive effect between richness and year, and between visitation rate and year on fruit proportion using a binomial generalized linear mixed model, and on the number of seeds employing a linear mixed model.
*P* values were obtained using the type III Anova (package: car CITAR) as recomended for tetsing interactions.
The number of seeds per fruit was centered and scaled per plant species to allow meaningful comparisons across species.
For all models, we included plant species identity nested within site and site as random effects because of multiple individuals of the same plant species are measured at each site.

@@

Stability of visitation rates ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 species (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
There is a strong positive relationship between stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increases [(Estimate ± standard error: 2.903 ± 1.134; *p* = 0.017) (Fig 2A)](Virginia%20me%20ha%20comentado%20en%20reportar%20el%20R2%20de%20los%20modelos%20pero%20al%20tratarse%20de%20modelos%20mixtos%20tendriamos%20que%20poner%20el%20marginal%20o%20el%20condicional.He%20revisado%20articulos%20que%20utilizan%20estos%20modleos%20y%20normalmente%20no%20ponen%20R2.%20Lo%20incluyo??), whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063; *p* = 0.986) (Fig 2B).
We also found a positive relationship between asynchrony and pollinator richness (0.020 ± 0.005, *p* = 0.001) (Fig 2C).
Furthermore, we observed one data point has a high leverage on the stability analysis (*C.crispus*, Fig 2A-B), when we remove this point, although the relationship is not significant, the tendency is still positive (0.968 ± 0.745; *p* = 0.215).

@@

Stability of fruit proportion varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged 1.28 to 55.86 (7.018 ± 1.441).
When we analyzed whether the stability of the pollinator's visitation rate affected the stability of the plant reproductive success, we did not find a clear relationship when analyzing the fruit proportion (Estimate ± standard error: -1.547 ± 2.611; *p* = 0.558) (Fig 3A).
However, contrary to expected, the stability of seed number did show a negative relationship with the stability of pollinator's visitation rate (-1.887 ± 0.959; *p* = 0.061) (Fig 3B).
Although this tendency is influenced by a high value in the stability of seed number of *H. halimifolium* (Fig 3B) since when we removed this point the relationship disappears (0.561 ± 0.535; *p* = 0.306).

@@

To analyse whether the variability of pollinator richness and visitation rate across years affected the reproductive success of plants we used all plant species sampled.
When we analysed the fruit proportion (set? unify terminology), we found that the interaction between year and pollinator richness, and year and visitation rate affected the fruit proportion (richness and year: $\chi 2$ = 28.976, df = 4, *p* = \<0.0001; visitation rate and year: $\chi 2$ = 40.691, df = 4, *p* = \<0.0001).
Furthermore, we observed a significant effect of year by itself, but not so of pollinator richness or visitation rate.
Although we observed a general saturation of the proportion of fruits developed with most species consistently over 80% of fruit set, in years like 2017 we found that a greater richness and visitation rate increased the fruit proportion.
We also observed a positive relationship between richness and fruit proportion in 2019.
However in 2018, the relationship between richness and fruit proportion was negative (Fig 3).
[esto requiere un poco más de story telling.Por ejemplo, estos años son años altos o bajos en polinizadores?](con%20los%20datos%20que%20tenemos%20la%20riqueza%20y%20la%20tasa%20de%20visitas%20es%20similar%20en%20los%20diferentes%20años.%20Tambien%20he%20mirado%20datos%20meteorologicos%20descargados%20de%20la%20estacion%20de%20Almonte-precipitacion,%20radiacion,%20humedad%20y%20temperatura,y%20no%20parace%20que%20haya%20diferencias%20entre%20años)

For the seed number analysis, we found an effect of year in both models in addition to the interaction between visitation rate and year ($\chi 2$ = 9.113, df = 4, *p* = 0.058) but not the interaction between pollinator richness and year ($\chi 2$ = 2.592, df = 4, *p* = 0.628).
We observed that a higher visitation rate increased the seed number in 2019 (Supplementary material-Fig 2).

@@

We show that pollinator's visitation rate stability increase with higher asynchrony of pollinators species abundances and that greater species richness only increase stability of visitation rate indirectly, via enhanced species asynchrony [IB: esto a abstract!]
.
However, contrary to expectations, we found no relationship between the stability of visitation rates and the stability of plant reproductive success.
This is because in our study system, plant reproduction is not pollinator limited in most years, with most plants reaching maximum reproductive success even in the sites with [lower pollinator abundances.](quizas%20decir%20lower%20richness%20and%20visitation%20rate??)
However, this do not imply that pollinators are not important or that are always in enough numbers to disregard them, because for specific years the relationship between pollinator activity and plant's reproductive output kicks in as important.[seria ideal decir quales... los que tienen poco polinizador? Los secos, quizas?](los%20años%20no%20tienen%20menor%20actividad%20ni%20riqueza%20de%20polinizadores,%20tampoco%20son%20los%20años%20mas%20secos,%20no%20se%20ven%20diferencias%20en%20precipitacion,%20temperatura,%20humedad%20o%20radiacion)
When and where pollinators are limiting is the key question then.

While drivers of temporal stability have been well study in plant communities [@Ruijven2007; @Gross2014; @Craven2018; @Leps2018; @Sasaki2019; @Valencia2020; @Kigel2021], relatively few studies have evaluated how this same drivers can affect community stability in mobile organisms such as pollinators [@Ebeling2008; @Senapathi2021; @Lazaro2022].
A first outcome of our analysis is that asynchrony of species abundances is a key driver of visitation rate stability.
This stability-asynchrony relationship has been found by different theoretical and empirical studies [@DeMazancourt2013; @Bluthgen2016; @Leps2018; @Sasaki2019; @Valencia2020; @Kigel2021].
For example, Lázaro et al.(2022) also found for plants, pollinators and their interactions that more asynchronous communities being more temporal stable.
In this sense, species asynchrony can increase temporal stability of visitation rate when the abundance of one species increases as a result of decreases in the abundance of another species (i.e. density compensation [@Winfree2009a; @Mukherjee2019]); or also when they respond differently to the same environmental changes (i.e. response diversity [@Walker99; @Winfree2013]).
[Aunque nosotros no sabemos si estos cambios son debido a perturbaciones ambientales, We believe it is important to test the degree to which these stabilizing mechanisms are at work.](Quizas%20añadir%20algo%20asi??)

On the other hand, species richness is considered one of the strongest drivers of community stability in plants [@Tilman2006; @Hallett2014], although Valencia et al. (2020), analyzing a large number of plant community datasets, have reported that this relationship is not as strong.
Pollinator studies carried out in crop systems have observed a positive relationship between species richness and stability of floral visits [@Ebeling2008] or stability of abundance and richness [@Senapathi2021].
However, our results show that pollinator richness was positively associated with asynchrony, which might positively affect the stability of visitation rate, but indirectly.
Species richness may increase the probability that community contains species with different responses to environmental conditions and perturbations, leading to asynchrony (compensation) among species abundance and thus, to an increase in community stability [@Craven2018; @McCann2000; @Yachi1999].

Despite the stability is crucial to the sustainability of ecosystem functions, relatively few studies have evaluated the stability of the pollinator visits frequency on pollination services, and those who did used agricultural systems [@Garibaldi2011; @Garibaldi2013; @Lazaro2019; @Hunicken2021].
To the best of our knowledge, how the stability of pollinator community affect to the reproductive success of the wild plant community remaining largely unknown.
In pollinator-dependent crops it has been observed that a greater yield stability is related to pollinator diversity and the stability of visitation rates [@Garibaldi2011; @Garibaldi2013; @Hunicken2021] but in our study system (wild plants), we did not find this relationship.
However, we observed that in specific years a higher visitation rate or richness of pollinators increases the proportion of fruits, even if there is a saturation of the proportion of fruits in most of the plant species analysed.
As the number of pollinator visits received by a plant increases from zero, the reproductive success of the plant is expected to rise initially but then to level off or possibly decline [@Young1992; @Morris2010].
Bees can remove 70--80% of the pollen that is presented in a flower and a flower's pollen can be exhausted after only a few visits.
Therefore, its reproductive success may not continue to increase with increased visitation, but instead may saturate quickly because of pollen depletion [@Thomson2001].
Even so, in certain years, the pollinator activity (visitation rate and richness) increases the fruit proportion.\

One possible explanation for this is that there was greater floral diversity and abundance in the plots these years, [although we have not measured this directly in the plots](quiero%20decir%20que%20nosotros%20no%20sabemos%20si%20esos%20años%20los%20plots%20tenian%20mas%20abundancia%20y%20diversidad%20de%20flores,%20recursos%20disponibles,%20nosotros%20tenemos%20las%20flores%20de%20las%20especies%20analizadas%20pero%20no%20del%20resto).
These factors can mediate pollination through impacts on pollinator densities [@Steffan-Dewenter2008a; @Williams2015], foraging dynamics [@Kunin1996], visitation rates [@VanNuland2013; @Veddeler2006], and pollen deposition [@Lortie1999; @Evans2017].
The concentration effect, which occurs when foragers visit a location in greater numbers due to high resource availability [@Kunin1996; @Totland1998], has an impact on the reproductive success of plants [@Blaauw2014; @Cohen2021].
Furthermore, some plant species increase pollinator visits to the coflowering plant, which subsequently contributes to the reproductive success of neighbouring individuals [@Schemske1981; @Moeller2004; @Ghazoul2006].
Another possible explanation to this might be the variations in abiotic factors.
Since the weather conditions can vary significantly between years, the abundance of pollinators during the flowering season of a plant can show annual variations, which may have an impact on the plant reproductive success [@Vicens2000; @Ivey2003].
In addition, the environmental conditions also affect to host plants.
For instance, the variation of temperature conditions lead to alterations in nectar production, composition and concentration [@Pacini2003], which can affect to the pollinator activity.
Although we have not taken these factors into account in our study, we believe it is important to include them in order to better understand the relationships between pollinators and plant reproductive success over time.
